### 2018-03-26 tex/paper.tex
Give a name to the web demo

The paper is structured like this: we begin in Section \ref{section:design} with a discussion of the design rationale for Marlowe, including an overview of the various approaches to scripting in blockchain as well as the different designs of the blockchains themselves. We conclude Section \ref{section:design} with a set of decisions about the blockchain environment for Marlowe. The central part of the paper is Section \ref{section:model} where we introduce the Marlowe model, including the assumptions made in designing 
it, the types of the principal functions and a description of the DSL as an algebraic type, constructor by constructor. Section \ref{section:example} presents an example of a larger Marlowe contract, for incentivised saving, and Section \ref{section:tool} introduces our tool for visualising and interacting with Marlowe contracts.
Section \ref{section:reflection} reflects on the system design, and observes some alternative designs and Section \ref{section:next-steps} enumerates the next steps for the project.

@@

One of the objectives of Marlowe is to be accessible to a wider audience
than a general purpose language would. With this aim, and to aid Marlowe's
usage by people that does not know is not familiar with its syntax,
we have developed a web tool that supports the interactive construction,
edition, and simulation of smart-contracts written in Marlowe. The
tool is publicly available in the url: \url{https://input-output-hk.github.io/scdsl/}.
In Figure~\ref{fig:full-screenshot-demo}, we provide a screenshot
of the tool in the middle of simulating the execution of the ``incentivised
saving'' contract described in Section~\ref{section:example}.

The tool has been mainly written in Haskell and compiled to JavaScript
by the Haste compiler~\cite{Haste}, it also relies on
the Blockly library~\cite{Blockly} for providing a visual
editor for smart contracts written in Marlowe. Blockly's editor allows
the user to visualise and edit smart-contracts as interlocking blocks
that can be dragged and dropped like pieces of a jigsaw puzzle (see
Figure~\ref{fig:detail-of-block}). The tool also provides functionality
to generate syntactically correct and formatted code (that is displayed
in the upper right corner of the application), and to convert the
code back to its block representation.

\begin{figure}
\begin{centering}
\includegraphics[width=1\textwidth]{pix/screenshot1}
\par\end{centering}
\caption{\label{fig:full-screenshot-demo}Screenshot of the visualisation tool
simulating the incentivised deposit contract.}
\end{figure}

@@

Additionally, to facilitate the introduction of inputs, the tool provides
two different interfaces:
\begin{itemize}
\item The manual interface (see Figure~\ref{fig:detail-of-manual-interface}),
provides a template for each of the four possible types of input:
commits, redeems, payment claims, and choices.
\item The smart interface (see Figure~\ref{fig:detail-of-smart-interface}),
calculates the possible operations that would make sense given the
current inputs, state of the contract, block number, and remaining
contract; and it provides them in a table with most of the parameters
already filled in.
\end{itemize}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.5]{pix/detail3}
\par\end{centering}
\caption{\label{fig:detail-of-manual-interface}Detail of the manual interface.}
\end{figure}

@@

Some degree of validation is provided by the visualisation tool presented in Section \ref{section:tool}, albeit for smaller-scale contracts, but there is a general question of how properties of contracts can be inferred. One relatively low-cost is to use QuickCheck-style property-based testing~\cite{quickCheck}, and properties developed here become candidates for fully fledged verification in a formalisation of the (semantics of) Marlowe.

>>>>

The paper is structured like this: we begin in Section \ref{section:design} with a discussion of the design rationale for Marlowe, including an overview of the various approaches to scripting in blockchain as well as the different designs of the blockchains themselves. We conclude Section \ref{section:design} with a set of decisions about the blockchain environment for Marlowe. The central part of the paper is Section \ref{section:model} where we introduce the Marlowe model, including the assumptions made in designing 
it, the types of the principal functions and a description of the DSL as an algebraic type, constructor by constructor. 
Section \ref{section:example} presents an example of a larger Marlowe contract, for incentivised saving, and Section 
\ref{section:tool} introduces Meadow, our tool for visualising and interacting with Marlowe contracts.
Section \ref{section:reflection} reflects on the system design, and observes some alternative designs and Section \ref{section:next-steps} enumerates the next steps for the project.

@@

One of the objectives of Marlowe is to be accessible to a wider audience
than a general purpose language would. With this aim, and to aid Marlowe's
usage by people that does not know is not familiar with its syntax,
we have developed Meadow, a web tool that supports the interactive construction,
edition, and simulation of smart-contracts written in Marlowe. The
tool is publicly available in the url: \url{https://input-output-hk.github.io/scdsl/}.
In Figure~\ref{fig:full-screenshot-demo}, we provide a screenshot
of Meadow in the middle of simulating the execution of the ``incentivised
saving'' contract described in Section~\ref{section:example}.

Meadow has been mainly written in Haskell and compiled to JavaScript
by the Haste compiler~\cite{Haste}, it also relies on
the Blockly library~\cite{Blockly} for providing a visual
editor for smart contracts written in Marlowe. Blockly's editor allows
the user to visualise and edit smart-contracts as interlocking blocks
that can be dragged and dropped like pieces of a jigsaw puzzle (see
Figure~\ref{fig:detail-of-block}). Meadow also provides functionality
to generate syntactically correct and formatted code (that is displayed
in the upper right corner of the application), and to convert the
code back to its block representation.

\begin{figure}
\begin{centering}
\includegraphics[width=1\textwidth]{pix/screenshot1}
\par\end{centering}
\caption{\label{fig:full-screenshot-demo}Screenshot of Meadow tool
simulating the incentivised deposit contract.}
\end{figure}

@@

Additionally, to facilitate the introduction of inputs, Meadow provides
two different interfaces:
\begin{itemize}
\item The manual interface (see Figure~\ref{fig:detail-of-manual-interface}),
provides a template for each of the four possible types of input:
commits, redeems, payment claims, and choices.
\item The smart interface (see Figure~\ref{fig:detail-of-smart-interface}),
calculates the possible operations that would make sense given the
current inputs, state of the contract, block number, and remaining
contract; and it provides them in a table with most of the parameters
already filled in.
\end{itemize}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.5]{pix/detail3}
\par\end{centering}
\caption{\label{fig:detail-of-manual-interface}Detail of the manual interface.}
\end{figure}

@@

Some degree of validation is provided by Meadow presented in Section \ref{section:tool}, albeit for smaller-scale 
contracts, but there is a general question of how properties of contracts can be inferred. One relatively low-cost is to 
use QuickCheck-style property-based testing~\cite{quickCheck}, and properties developed here become candidates for 
fully fledged verification in a formalisation of the (semantics of) Marlowe.
